Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-25 BN_discretizer_paper.tex
Do Tim's comments and Find a typo

\subsubsection{Evaluation of $P(D_{C_j} \mid \Lambda, D_{\bm{S}_j})$}
Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_{\bm{S}}^{(j)}$ be the number of instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,\ell}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $\ell$th instantiation of $\bm{S}_j$.
Let ${n^{(j)}_{i,\ell} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,\ell}}$.
\tim{Is this correct: Note that ${\gamma_i = \sum_l n^{(j)}_{i,\ell}}$ for all $j$.}
It follows that

@@

The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one}, and~\ref{eq:likelihood_three}.
\tim{Why not Eq~\ref{eq:likelihood_two}?}
The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:

\begin{equation}
\label{eq:opt_prob}
\begin{aligned}
  & \sum_{i=1}^{k-1}
   - \ln
    \paren{
      1 - \exp
      \paren{
        - L \cdot  \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
      + \sum_{i=1}^{k}
      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} + \\
  & \sum_{i=1}^{k} \brock{
  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
  +{ \ln \paren{
        \frac{
          {\gamma_i}!
        }{
          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
        }
      }}
  } \\
  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
  { \ln
          {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
    +
    \ln \paren{ {
          \frac{
            {n^{(j)}_{i,\ell}}!
          }{
            {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
          }
        }
        } }
\end{aligned}
\end{equation}

>>>>

\subsubsection{Evaluation of $P(D_{C_j} \mid \Lambda, D_{\bm{S}_j})$}
Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_{\bm{S}}^{(j)}$ be the number of instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,\ell}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $\ell$th instantiation of $\bm{S}_j$.
Let ${n^{(j)}_{i,\ell} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,\ell}}$.
Note that ${\gamma_i = \sum_{\ell} n^{(j)}_{i,\ell}}$ for all $j$.
It follows that

@@

The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one},~\ref{eq:likelihood_two} and~\ref{eq:likelihood_three}.
The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:

\begin{equation}
\label{eq:opt_prob}
\begin{aligned}
  & \sum_{i=1}^{k-1}
   - \ln
    \paren{
      1 - \exp
      \paren{
        - L \cdot  \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
      + \sum_{i=1}^{k}
      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} + \\
  & \sum_{i=1}^{k} \brock{
  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
  +{ \ln \paren{
        \frac{
          {\gamma_i}!
        }{
          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
        }
      }}
  } + \\
  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
  { \ln
          {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
    +
    \ln \paren{ {
          \frac{
            {n^{(j)}_{i,\ell}}!
          }{
            {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
          }
        }
        } }
\end{aligned}
\end{equation}
